Resources on spatial models

### 2022-10-27 docs/resources.Rmd
Typo

* [Exact sparse CAR models in Stan](https://mc-stan.org/users/documentation/case-studies/mbjoseph-CARStan.html)
* [Spatial Models in Stan: Intrinsic Auto-Regressive Models for Areal Data](https://mc-stan.org/users/documentation/case-studies/icar_stan.html)
* [Spatial Smoothing in Stan: Conditional Auto-Regressive Models](https://insp.memberclicks.net/assets/docs/Local_Events/2018/Paris/Stanforpmx2018_MitziMorris.pdf)
* [Fast CAR: Two weird tricks for fast conditional autoregressive models in Stan](https://statmodeling.stat.columbia.edu/2016/09/02/two-weird-tricks-for-fast-conditional-autoregressive-models-in-stan/)
* [feature/car in `rstanarm``](https://github.com/stan-dev/rstanarm/issues/207)
* [Writing Stan programs for use with the loo package](https://mc-stan.org/loo/articles/loo2-with-rstan.html)

>>>>

* [Exact sparse CAR models in Stan](https://mc-stan.org/users/documentation/case-studies/mbjoseph-CARStan.html)
* [Spatial Models in Stan: Intrinsic Auto-Regressive Models for Areal Data](https://mc-stan.org/users/documentation/case-studies/icar_stan.html)
* [Spatial Smoothing in Stan: Conditional Auto-Regressive Models](https://insp.memberclicks.net/assets/docs/Local_Events/2018/Paris/Stanforpmx2018_MitziMorris.pdf)
* [Fast CAR: Two weird tricks for fast conditional autoregressive models in Stan](https://statmodeling.stat.columbia.edu/2016/09/02/two-weird-tricks-for-fast-conditional-autoregressive-models-in-stan/)
* [feature/car in `rstanarm`](https://github.com/stan-dev/rstanarm/issues/207)
* [Writing Stan programs for use with the loo package](https://mc-stan.org/loo/articles/loo2-with-rstan.html)
